
\begin{thebibliography}{00}


% \bibitem{b3} J. U. Duncombe, ``Infrared navigation---Part I: An assessment of feasibility,'' \emph{IEEE Trans. Electron Devices}, vol. ED-11, no. 1, pp. 34--39, Jan. 1959, 10.1109/TED.2016.2628402.

\bibitem{b1} L. Li, Y. Sun, Z. Liu, X. Hou, G. Shi, and M. Su, ``A Decentralized Control with Unique Equilibrium Point for Cascaded-Type Microgrid,” \emph{IEEE Trans. Sustain. Energy}, vol. 10, no. 1, pp. 324-326, 2019, doi: 10.1109/TSTE.2018.2871641.

\bibitem{b2} A. Reinders et al., ``An Exploration of the Three-Layer Model Including Stakeholders, Markets and Technologies for Assessments of Residential Smart Grids,” \emph{Appl. Sci.}, vol. 8, no. 12, p. 23-63, 2018, doi: 10.3390/app8122363.

\bibitem{b3} A. F. Crossland, D. Jones, N. S. Wade, and S. L. Walker, ``Comparison of the location and rating of energy storage for renewables integration in residential low voltage networks with overvoltage constraints,” \emph{Energies}, vol. 11, no. 8, p. 2041, 2018, doi: 10.3390/en11082041.

\bibitem{b4} Y. Sun, X. Hou, J. Yang, H. Han, M. Su and J. M. Guerrero, ``New Perspectives on Droop Control in AC Microgrid," \emph{IEEE Transactions on Industrial Electronics}, vol. 64, no. 7, pp. 5741-5745, July 2017, doi: 10.1109/TIE.2017.2677328.


\bibitem{b5-wind-data} C. Draxl, A. Clifton, B.-M. Hodge, and J. McCaa, The wind integration national dataset (WIND) toolkit, \emph{Applied Energy}, vol. 151, pp. 355366, 2015.

\bibitem{b6} 
N. Uribe-Pérez, L. Hernández, D. de la Vega, and I. Angulo, ``State of the Art and Trends Review of Smart Metering in Electricity Grids,” \emph{Appl. Sci.}, vol. 6, no. 3, pp. 1–24, 2016, doi: 10.3390/app6030068.

% N. Uribe-Pérez, L. Hernández, D. de la Vega, and I. Angulo, “State of the Art and Trends Review of Smart Metering in Electricity Grids,” Appl. Sci., vol. 6, no. 3, pp. 1–24, 2016.


% \item \emph{Basic format for reports:}\\
% \bibitem{b18} R. J. Hijmans and J. van Etten, ``Raster: Geographic analysis and modeling with raster data,'' R Package Version 2.0-12, Jan. 12, 2012. [Online]. Available: \underline {http://CRAN.R-project.org/package=raster} 

% \bibitem{b19} Teralyzer. Lytera UG, Kirchhain, Germany [Online].
% Available:
% \underline{http://www.lytera.de/Terahertz\_THz\_Spectroscopy.php?id=home}, Accessed on: Jun. 5, 2014

\bibitem{b7} ``Krabi Goes Green: Towards A Model Town, With More Than 100\% Renewable Energy,'' Greenpeace Southeast Asia, Thailand, 2018 [Online]. 
Available: \underline{https://www.greenpeace.or.th/report/Krabi-goes-green-EN.pdf}, Accessed on: Oct. 8, 2020


\bibitem{b8} U. Datta, A. Kalam, and J. Shi, “Battery energy storage system for aggregated inertia-droop control and a novel frequency dependent state-of-charge recovery,” \emph{Energies}, vol. 13, no. 8, 2020.

\bibitem{b9} C. Li et al., “Comprehensive review of renewable energy curtailment and avoidance: A specific example in China,” \emph{Renew. Sustain. Energy Rev.}, vol. 41, pp. 1067–1079, 2015.

\bibitem{b10} J. Wu, B. Zhang, H. Li, Z. Li, Y. Chen, and X. Miao, “Statistical distribution for wind power forecast error and its application to determine optimal size of energy storage system,” \emph{Int. J. Electr. Power Energy Syst.}, vol. 55, pp. 100–107, 2014.

\bibitem{b11} 	
N. Jayasekara, M. A. S. Masoum and P. J. Wolfs, ``Optimal Operation of Distributed Energy Storage Systems to Improve Distribution Network Load and Generation Hosting Capability," \emph{IEEE Trans. Sustainable Energy}, vol. 7, no. 1, pp. 250-261, Jan. 2016, doi: 10.1109/TSTE.2015.2487360.
% Jayasekara, N., Member, S., Masoum, M. A. S., Member, S., Wolfs, P. J., and Member, S., “Optimal Operation of Distributed Energy Storage Systems to Improve Distribution Network Load and Generation Hosting Capability.,” pp. 1–12, 2015.


\bibitem{b12} 
R. Fernández-Blanco, Y. Dvorkin, B. Xu, Y. Wang and D. S. Kirschen, ``Optimal Energy Storage Siting and Sizing: A WECC Case Study," \emph{IEEE Trans. Sustainable Energy}, vol. 8, no. 2, pp. 733-743, April 2017, doi: 10.1109/TSTE.2016.2616444.



\bibitem{13-main_barrier_ESS}
J. L. Lorente, X. A. Liu, R. Best, and D. J. Morrow, “Energy storage allocation in power networks - A state-of-the-art review,” \emph{Proc. - 2018 53rd Int. Univ. Power Eng. Conf. UPEC 2018}, 2018.

\bibitem{b14}
H. Bludszuweit, J. A. Dominguez-Navarro and A. Llombart, ``Statistical Analysis of Wind Power Forecast Error," \emph{IEEE Transactions on Power Systems}, vol. 23, no. 3, pp. 983-991, Aug. 2008, doi: 10.1109/TPWRS.2008.922526.

\end{thebibliography}